### 2016-09-30 Projects/DelCo_2012/Report/DelCo_2012.tex
Final copy of hose stream report; minor edits to CAF and burner reports

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note XXXX}
\end{flushright}

@@

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
\endgroup
}

@@

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup

@@

\large
\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (August 2016) \\
% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
CODEN: NTNOEF }

@@

\begingroup
{\bf This publication is available free of charge from:}
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{\bf http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup

@@

\vspace{0.5in}
Key words: compressed air foam, fire experiments, fire fighting, fire suppression, fuel load, gas cooling, structural fire fighting, suppression research

>>>>

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note 1927}
\end{flushright}

@@

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1927}{http://dx.doi.org/10.6028/NIST.TN.1927}
\endgroup
}

@@

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1927}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup

@@

\large
\flushright{\bf National Institute of Standards and Technology Technical Note 1927 \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~1927, \pageref{LastPage} pages (August 2016) \\
CODEN: NTNOEF }

@@

\begingroup
{\bf This publication is available free of charge from:}
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1927}{\bf http://dx.doi.org/10.6028/NIST.TN.1927} \\
\endgroup

@@

\vspace{0.5in}
Keywords: compressed air foam, fire experiments, fire fighting, fire suppression, fuel load, gas cooling, structural fire fighting, suppression research

### 2016-09-30 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Final copy of hose stream report; minor edits to CAF and burner reports

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note XXXX}
\end{flushright}

\headerB{
Impact of Hose Streams on Air Flows inside a Structure \\
}

@@

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
\endgroup
}

@@

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note XXXX}
\end{flushright}

\headerB{
Impact of Hose Streams on Air Flows inside a Structure
}

@@

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup

@@

\large
\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (September 2016) \\
% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
CODEN: NTNOEF }

@@

\begingroup
{\bf This publication is available free of charge from:}
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1838}{\bf http://dx.doi.org/10.6028/NIST.TN.1838} \\
\endgroup

@@

\begin{tabbing}
\hspace{1.5in} \= \\
ESTC \> Delaware County Emergency Services Training Center \\
NF \> Narrow Fog Stream\\
NIST \> National Institute of Standards and Technology \\
SB \> Smooth Bore Stream\\
SS \> Straight Stream \\
UL FSRI \> Underwriters Laboratories Firefighter Safety Research Institute \\
WF \> Wide Fog Stream \\
\end{tabbing}

@@

@@

\section{Experimental Setup}
\label{sec:exp_setup}
The series of field experiments described in this report were conducted in two structures of similar design located at the Delaware County Emergency Services Training Center (ESTC) in Sharon Hill, PA. Differential pressure and temperature sensors were installed at ventilation points throughout the test structures to determine air velocity during the water flow experiments.

@@

The second floor of the Two Story Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell. The walls of the second floor were wood-frame with nominal 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers. The interior walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) durarock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board. The interior ceiling of the second story was covered by two layers of 13~mm (0.5~in) thick cement board. The exterior walls were protected with 11~mm (0.44~in) thick OSB and 8~mm (0.31~in) fiber cement lap siding.

>>>>

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note 1938}
\end{flushright}

\headerB{
Impact of Hose Streams on Air Flows Inside a Structure \\
}

@@

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1938}{http://dx.doi.org/10.6028/NIST.TN.1938}
\endgroup
}

@@

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note 1938}
\end{flushright}

\headerB{
Impact of Hose Streams on Air Flows Inside a Structure
}

@@

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1938}{http://dx.doi.org/10.6028/NIST.TN.1938} \\
\endgroup

@@

\large
\flushright{\bf National Institute of Standards and Technology Technical Note 1938 \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~1938, \pageref{LastPage} pages (September 2016) \\
CODEN: NTNOEF }

@@

\begingroup
{\bf This publication is available free of charge from:}
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1938}{\bf http://dx.doi.org/10.6028/NIST.TN.1938} \\
\endgroup

@@

\begin{tabbing}
\hspace{1.5in} \= \\
NF \> Narrow Fog Stream\\
NIST \> National Institute of Standards and Technology \\
OSB \> Oriented Strand Board \\
SB \> Smooth Bore Stream\\
SS \> Straight Stream \\
TJI \> Truss Joist I-beams \\ 
UL FSRI \> Underwriters Laboratories Firefighter Safety Research Institute \\
WF \> Wide Fog Stream \\
\end{tabbing}

@@

\vspace{0.5in}
Keywords: fire fighting, fire suppression, hose streams, nozzles, ventilation

@@

\section{Experimental Setup}
\label{sec:exp_setup}
The series of field experiments described in this report were conducted in two structures of similar design located at the Delaware County Emergency Services Training Center in Sharon Hill, Pennsylvania. Differential pressure and temperature sensors were installed at ventilation points throughout the test structures to determine air velocity during the water flow experiments.

@@

The second floor of the Two Story Structure was built on the structure's first floor wood ceiling support. The two floors were connected by an interior stairwell. A door made of lauan plywood was located at the top of the stairwell. The walls on the second floor were of wood-frame with 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers. Two layers of 16~mm (0.63~in) Type X gypsum board lined the interior side of the wood studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board. The interior ceiling of the second story was covered by two layers of 13~mm (0.5~in) thick cement board. The exterior sides of the outer walls on the second floor were protected by 11~mm (0.44~in) thick OSB and 8~mm (0.31~in) fiber cement lap siding.
